Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-08 ms.tex
move f_1 map figures to more appropriate location

With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
stringent prior, but we must restrict the fit from wandering with too much
freedom, as we are attempting to constrain three parameters using an SED
with only seven intensity measurements.

% add comment about high f_1 regions near NGP

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} The results of our low-resolution fit with $f_1$
allowed to vary, but with a strong prior 
$P(f_1)=\mathcal{N}(f_1|0.0363, 0.003)$.}
\end{center}
\end{figure}

>>>>

With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
stringent prior, but we must restrict the fit from wandering with too much
freedom, as we are attempting to constrain three parameters using an SED
with only seven intensity measurements. To boost S/N, we have performed
the fits using maps smoothed to $1^{\circ}$ resolution.

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} The results of our low-resolution fit with $f_1$
allowed to vary.}
\end{center}
\end{figure}

The resulting full-sky map of $f_1$ is shown in Figure \ref{}. Some of the most

% add comment about high f_1 regions near NGP
% also add sentences referring reader to the two f_1 figures

@@
